\documentclass{article}
\begin{document}

\author{somekenyan}
\title{MangaDownloader document}
\maketitle

\section{Introduction}

This document is to show me what I have implemented in the mangadownloader program. Currently I am working on only downloading from mangapanda

\section{Modules}
These are the small pieces of the program that will be combined to get the big program

\begin{itemize}
\item Download images
It should download an image from a page, give it an approppriate name depending on the page number and then save it to the appropriate folder
\item Download manga chapter
This should be able to download a complete manga, going through the pages and getting all the pages
\item List episodes
This should be able to list various chapters of the manga
\item List anime
This should be able to list all the anime manga in the site
\end{itemize}

\subsection{Manga downloader}
Trying to divide the application to very small manageable pieces such that I can try my best to become better organized.
The main components of this should be:
\begin{itemize}
\item List all the manga titles of the site
\item Access a particular manga and list all the chapters available in the site
\item Download the chapters of a particular selected manga
\item Save manga in a folder. Perhaps use zip format to maintain the size
\end{itemize}

\subsection{Manga reader}
\begin{itemize}
\item Access a folder and see whether it has manga or has various chapters
\item Read images in a folder based on their sequence in the manga
\end{itemize}

\subsection{XML parsing}

THe details of the tags to be used while parsing a page will be stored in an XML file. This will help later on when I decide to add other manga sites.

\section{Planning}
Research shall be done depending on what submodule is being worked on. After research implementation should take place immediately after. Documentation should be done along the way too.

\subsection{XML and downloading}
I am using the xml.dom.minidom package for parsing through xml. 
I want to access the site and list the chapters for one piece using xmlparser and a downloader I will wirte. For modularity, I will also try the same for another site

I can already download images although still not sure about the saving of the images.

I get a list of all the chapters. This will then be passed to imagedownload function downloading the images sequentially

I can get the link of the image to be downloaded from the site.

\section(Coding)
I will save the manga downloaded in cbz format. With this, I implemented a module named cbrmaker to do this. This way, I will not need to write a manga reader as the default document viewer can be used to view the manga.

\end{document}
